\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-15 ms.tex
david n suggestions

\changes{The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and
with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to calibrate the photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---much larger than the uncertainty in the individual photometry---is due to the large differences in the DECam and SkyMapper u-band passbands.}

@@

\figurename~\ref{fig:decam-cmd} shows \decam\ color-magnitude diagrams for the control and cluster sub-fields (the magnitudes here are not extinction-corrected).
We find that the $u$-band data were too shallow to be useful for this work, so restrict the further analysis in this work to the $g$- and $i$-bands.
The blue comoving group, \clustername, identified in \sectionname~\ref{sec:discovery} using \gaia\ data alone shows up as a clear young main sequence in the cluster fields (right panel of \figurename~\ref{fig:decam-cmd}).
Later, we use photometry in the sub-region of the cluster fields identified by the dashed rectangle to infer the cluster parameters.

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation Equations\label{tbl:transphot}}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term} & \colhead{RMS}
}
\startdata
$u$  &  $g-i$ & 2.17820 $\pm$   0.016 &     \nodata  & 0.164 \\
$g$  & $g-r$ & $-0.052868 \pm  0.0068$  &     $-0.034937 \pm 0.0051$  &  0.028 \\
$i$   &  $i-z$ & $-0.246645 \pm 0.0011$ &     $-0.07379 \pm 0.00069$  &  0.028
\enddata
\end{deluxetable}
\end{center}

@@

We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.
In the outskirts of the SMC, the metallicity distribution of the youngest stars ($\textrm{age} < 2~\textrm{Gyr}$) has a peak around $\feh \sim -1$ and a spread of $\sigma_{\feh} \sim 0.2~\textrm{dex}$, which at least means that the metallicity of \clustername\ ($\feh \approx -1.1$) is consistent with young SMC stars \citep{Dobbie:2014}.

>>>>

\changes{The instrumental photometry (i.e., $-2.5\log(\texttm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to derive color transformations relating our instrumental DECam photometry to calibrated SkyMapper u- and PS1 grizy photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to put our photometry on the SkyMapper/PS1 system, enabling us to treat this photometry as if it were PS1/SkyMapper photometry in the isochrone modeling.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---much larger than the uncertainty in the individual photometry---is due to the large differences in the DECam and SkyMapper u-band passbands.}

@@

\figurename~\ref{fig:decam-cmd} shows \decam\ color-magnitude diagrams for the control and cluster sub-fields (the magnitudes here are not extinction-corrected).
% We find that the $u$-band data were too shallow to be useful for this work, so restrict the further analysis in this work to the $g$- and $i$-bands.
The blue comoving group, \clustername, identified in \sectionname~\ref{sec:discovery} using \gaia\ data alone shows up as a clear young main sequence in the cluster fields (right panel of \figurename~\ref{fig:decam-cmd}).
Later, we use photometry in the sub-region of the cluster fields identified by the dashed rectangle to infer the cluster parameters.

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation Equations\label{tbl:transphot}}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term}
}
\startdata
% $u$  &  \nodata & $2.178 \pm  0.016$ &     \nodata \\
% $g$  & $g-r$ & $-0.05287 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
% $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
$u$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
$g$  & $g-r$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
$i$   &  $i-z$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
\enddata
\end{deluxetable}
\end{center}

@@

We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances ($\[O/H\] \sim -1$) suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.
In the outskirts of the SMC, the metallicity distribution of the youngest stars ($\textrm{age} < 2~\textrm{Gyr}$) has a peak around $\feh \sim -1$ and a spread of $\sigma_{\feh} \sim 0.2~\textrm{dex}$, which at least means that the metallicity of \clustername\ ($\feh \approx -1.1$) is consistent with young SMC stars \citep{Dobbie:2014}.
